Robust background subtraction in traffic environments

### 2019-02-18 paper/Paper.tex

\subsection*{T}
The controller $T(x_i)$ associated to each pixel, is introduced with the idea to change dinamically the learning rate associated to each pixel based on its classification. It is slowly increased when the pixel is classified as background and slowly decreased when the pixel is classified as foreground. That leads to have a better foreground detection for multiple reasons. \newline
In case of highly dynamic background (i.e. big $\overline{d}_{min}(x_i)$), the learning parameter $T(x_i)$ stays constant or only slightly changes. In this case of highly dynamic background, erroneously detected foreground will not remain for long, be-
cause the probability to update $p = 1/T(x_i)$ does not reach
zero too fast. \newline
In the other ideal case of a fully static background, a classification as foreground is quite solid. \newline
$T_{upper}, T_{lower}:$ control respectively the lowest and the highest probability of updating a pixel and putting it in the
background model $B$. \newline
$T_{inc}, T_{dec}:$ are fixed parameters and control the update of the controller T of each pixel, has been chosen to differentiate the two quantity since the pixels that are background are usually the largest part so choosing different parameters can lead to a better perfomance.\newline
Since one of the objective of the work is to have a robust classification of the foreground objects, we want to find the best values for the T parameters such that an object if classified as foreground stay as it for the longest period of time. INSERIRE IMMAGINI

@@

>>>>

\subsection*{T}
The controller $T(x_i)$ associated to each pixel, is introduced with the idea to change dinamically the learning rate associated to each pixel based on its classification. It is slowly increased when the pixel is classified as background and slowly decreased when the pixel is classified as foreground. That leads to have a better foreground detection for multiple reasons. \newline
In case of highly dynamic background (i.e. big $\overline{d}_{min}(x_i)$), the learning parameter $T(x_i)$ stays constant or only slightly changes. In this case of highly dynamic background, erroneously detected foreground will not remain for long, be-
cause the probability to update $p = 1/T(x_i)$ does not reach
zero too fast. \newline
In the other ideal case of a fully static background, a classification as foreground is quite solid. \newline
$T_{upper}, T_{lower}:$ control respectively the lowest and the highest probability of updating a pixel and putting it in the
background model $B$. \newline
$T_{inc}, T_{dec}:$ are fixed parameters and control the update of the controller T of each pixel, has been chosen to differentiate the two quantity since the pixels that are background are usually the largest part so choosing different parameters can lead to a better perfomance.\newline
Since one of the objective of the work is to have a robust classification of the foreground objects, we want to find the best values for the T parameters such that an object if classified as foreground stay as it for the longest period of time. 
\begin{figure}[!t]
    \centering
    \subfloat[][$T_{inc}$ = 1]{
        \includegraphics[width=0.45\textwidth]{Figures/T_inc_1.png}
    }
    \newline
    \subfloat[][$T_{inc}$ = 5]{
        \includegraphics[width=0.45\textwidth]{Figures/T_inc_5.png}
    }
    \caption{Have an higher $T_{inc}$ means decreasing faster the probability that a pixel is included in the background model once it is classified as foreground. Clearly visible in the two image reporting a car stopped for $30s$.}
\end{figure}

@@

\subsection{Post-processing}
To enhance the performance of the algorithm is applied on the final mask a median-filter using a square kernel. Since the value of the pixels can be 0 or 255 is equivalent to perform a majority voting among the kernel's pixels to decide the value of the middle one. That has shown to reduce the noise on the final mask and in the meanwhile generate more connected components. The size chosen for the kernel after different experiments is $5\times 5$.

\begin{figure}
\includegraphics[width=\linewidth]{Figures/median_blur.png}
\caption{Comparison between output whitout post-processing 			and with median-blur post-processing}
\end{figure}
